Gafo-cc data processing

### 2024-01-15 analysis/gafo-cc-data-processing.Rmd
update supplement

tidy_demographics_cong <- raw_demographics_cong %>%
  filter(birth_date != "NA")%>%
  filter(status == "keep", id != "BD000001", id != "BY000001")%>%
  mutate(
    test_date = as.Date(as.character(test_date), format = "%Y%m%d"),
    birth_date = as.Date(as.character(birth_date), format = "%Y%m%d"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
    screen = ifelse(screen == "fallaci", 0, 1), 
    touchscreen = ifelse(touchscreen == "fallaci", 0, 1),
    household = as.numeric(household), 
    children = as.numeric(children),
    younger_children = as.numeric(younger_children)
  )  %>%
  select(-c(first_name, last_name, test_date, birth_date, comment))%>%
  #filter(!is.na(ageinyears))%>%
  rename(subjid = id)

@@

# Merge
```{r}
merge_raw_data <- bind_rows(
  data_zambia,
  data_namibia%>%rename(younger_children = youngerchildren),
  data_leipzig,
  data_nigeria,
  data_plymouth,
  data_stanford,
  data_mex,
  data_china, 
  data_arg,
  data_ind,
  data_nz, 
  data_tur,
  data_cong,
  data_uganda
)%>%
  #mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
  filter(trialtype == "test",
         voiceover == F
         )%>%
  mutate(age_group = substr(ageinyears, 1,1), 
         trialnr = as.numeric(factor(trialnr)))

write_csv(merge_raw_data,"../data/gafo-cc-raw-data.csv")

data <- merge_raw_data%>%
  select(subjid, community, age_group, ageinyears, sex, screen, touchscreen, household, children, younger_children, trialnr, targetposition,targetcenterx, targetcentralityx, clickdistfromtargetcenterx)%>%
  filter(ageinyears > 1)

>>>>

tidy_demographics_cong <- raw_demographics_cong %>%
  filter(birth_date != "NA")%>%
  filter(status == "keep", id != "BD000001", id != "BY000001")%>%
  mutate(
    test_date = as.Date(as.character(test_date), format = "%Y%m%d"),
    birth_date = as.Date(as.character(birth_date), format = "%Y%m%d"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
    #screen = ifelse(screen == "fallaci", 0, 1), 
    #touchscreen = ifelse(touchscreen == "fallaci", 0, 1),
    household = as.numeric(household), 
    children = as.numeric(children),
    younger_children = as.numeric(younger_children)
  )  %>%
  select(-c(first_name, last_name, test_date, birth_date, comment))%>%
  #filter(!is.na(ageinyears))%>%
  rename(subjid = id)

@@

# Merge
```{r}
merge_raw_data <- bind_rows(
  data_zambia,
  data_namibia%>%rename(younger_children = youngerchildren),
  data_leipzig,
  data_nigeria,
  data_plymouth,
  data_stanford,
  data_mex,
  data_china, 
  data_arg,
  data_ind,
  data_nz, 
  data_tur,
  data_cong,
  data_uganda
)%>%
  #mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
  filter(trialtype == "test",
         voiceover == F
         )%>%
  mutate(age_group = substr(ageinyears, 1,1), 
         trialnr = as.numeric(factor(trialnr)), 
         sex = ifelse(sex == "F", "f", sex),
         sex = ifelse(sex == "female", "f", sex),
         sex = ifelse(sex == "male", "m", sex),
         sex = ifelse(sex == "NaN", NA, sex), 
         screen = ifelse(touchscreen == 1, 1, screen),
         household = ifelse(household == "NaN", NA, household),
         children = ifelse(children == "NaN", NA, children),
         younger_children = ifelse(younger_children == "NaN", NA, younger_children))

# Quality checks

```{r}
# data checks

## communities
unique(merge_raw_data$community)

## age ranges
range(merge_raw_data$ageinyears)

## sex  
unique(merge_raw_data$sex)

## screen and touchscreen
unique(merge_raw_data$screen)
unique(merge_raw_data$touchscreen)
# check NAs
merge_raw_data%>%
  filter(is.na(screen), trialnr == 1)

merge_raw_data%>%
  filter(is.na(touchscreen), trialnr == 1)

### check if there are cases that say they don't have a screen but do say they have a touch screen 
merge_raw_data%>%
  filter(screen == 0 & touchscreen == 1, trialnr == 1)

# household
unique(merge_raw_data$household)

merge_raw_data%>%
  filter(is.na(household), trialnr == 1)

# children 
unique(merge_raw_data$children)
## check number of children - should include the one being tested, therefore cannot be 0
merge_raw_data%>%
  filter(children == 0, trialnr == 1)

## check if there are cases with more younger children than children (cannot be)

merge_raw_data%>%
  filter(children < younger_children, trialnr == 1)

merge_raw_data%>%
  filter(children == younger_children, trialnr == 1)

```{r}
write_csv(merge_raw_data,"../data/gafo-cc-raw-data.csv")
```

```{r}
data <- merge_raw_data%>%
  select(subjid, community, age_group, ageinyears, sex, screen, touchscreen, household, children, younger_children, trialnr, targetposition,targetcenterx, targetcentralityx, clickdistfromtargetcenterx)%>%
  filter(ageinyears > 1)
